\documentclass{article}
\usepackage{amsfonts}

\begin{document}
\title{Black survey}
\date{}
\maketitle
\section*{}
The intent of this survey is to approximately determine the extent of the knowledge of the people in black. Next to each item, write
a nonnegative integer less than or equal to $3$, where each number roughly corresponds to the following:
\begin{enumerate}
\item[0.] You have no idea what this item is referring to and haven't heard of it.
\item[1.] You have heard of it, but have never used it or seen many uses of it.
\item[2.] You have used before several times this and/or have a pretty good idea what this is.
\item[3.] You know this quite well, and/or have used it or things related to it quite often.
\end{enumerate}

Note that these are only rough guidelines, 
\subsection*{Combinatorics}
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Binomial coefficients (Number of ways to choose $k$ elements from an $n$ element set).
\item[\underline{\hspace{0.4cm}}] Invariants/monovariants.
\item[\underline{\hspace{0.4cm}}] Expected values.
\item[\underline{\hspace{0.4cm}}] Inclusion-exclusion.
\item[\underline{\hspace{0.4cm}}] Probabilistic method.
\item[\underline{\hspace{0.4cm}}] Double counting/reversing the order of summation.
\item[\underline{\hspace{0.4cm}}] Extremal principle.
\item[\underline{\hspace{0.4cm}}] Burnside's lemma.
\end{enumerate}

\subsection*{Analysis/Algebra}
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Vieta's formulas.
\item[\underline{\hspace{0.4cm}}] Fundamental theorem of algebra.
\item[\underline{\hspace{0.4cm}}] Fields, rings, groups. 
\item[\underline{\hspace{0.4cm}}] Convexity.
\item[\underline{\hspace{0.4cm}}] Cauchy Schwarz, AM-GM, Jensen, etc.
\item[\underline{\hspace{0.4cm}}] Supremums, infimums.
\item[\underline{\hspace{0.4cm}}] Calculus (in $\mathbb{R}$).
\item[\underline{\hspace{0.4cm}}] Generating functions.
\end{enumerate}

\subsection*{Geometry}
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Similar triangles.
\item[\underline{\hspace{0.4cm}}] Coordinate bashing.
\item[\underline{\hspace{0.4cm}}] Complex bashing.
\item[\underline{\hspace{0.4cm}}] Cyclic quads. 
\item[\underline{\hspace{0.4cm}}] Cross ratios.
\item[\underline{\hspace{0.4cm}}] Homothety.
\item[\underline{\hspace{0.4cm}}] Spiral similarity.
\item[\underline{\hspace{0.4cm}}] Inversion.
\item[\underline{\hspace{0.4cm}}] Radical axes.
\item[\underline{\hspace{0.4cm}}] Poles, polars.
\end{enumerate}

\subsection*{Number theory}
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Working modulo $n$.
\item[\underline{\hspace{0.4cm}}] Fermat's little theorem.
\item[\underline{\hspace{0.4cm}}] Orders/primitive roots.
\item[\underline{\hspace{0.4cm}}] Multiplicativity
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Dirichlet convolutions
\item[\underline{\hspace{0.4cm}}] M\"{o}bius inversion
\end{enumerate}
\item[\underline{\hspace{0.4cm}}] Euclidean algorithm.
\item[\underline{\hspace{0.4cm}}] Bezout's lemma.
\item[\underline{\hspace{0.4cm}}] Fundamental theorem of arithmetic in $\mathbb{Z}$ (unique factorization).
\item[\underline{\hspace{0.4cm}}] Extensions of $\mathbb{Z}$ ($\mathbb{Z}[i], \mathbb{Z}[\omega]$).
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Fundamental theorem of arithmetic in extensions of $\mathbb{Z}$.
\end{enumerate}
\item[\underline{\hspace{0.4cm}}] Roots of unity.
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Cyclotomic polynomials.
\item[\underline{\hspace{0.4cm}}] Automorphisms of $\mathbb{Q}(\zeta_n)$.
\end{enumerate}
\item[\underline{\hspace{0.4cm}}] Hensel Lifting.
\item[\underline{\hspace{0.4cm}}] $\mathbb{Q}_p$.
\item[\underline{\hspace{0.4cm}}] Vieta jumping.
\end{enumerate}

\subsection*{Miscellaneous}
\begin{enumerate}
\item[\underline{\hspace{0.4cm}}] Infinite descent.
\item[\underline{\hspace{0.4cm}}] Set theory.
\item[\underline{\hspace{0.4cm}}] Induction.
\item[\underline{\hspace{0.4cm}}] Strong induction.
\end{enumerate}
\end{document}
